---
title: "P8105 Homework 1"
author: "Bingkun Luo"
date: "9/14/2019"
output:html_document:
    toc: true
    toc_float: true
---
# Question 1
## a
```{r}
library(tidyverse)
df_1 = tibble(samp= rnorm(8),
              vec_logical = samp > 0,
              vec_chara = c("a","a","a","a","a","a","a","a"),
              vec_factor = factor(c("low","high","medium","high","low","medium", "high","low"),levels = c("low",              "medium","high"))
              )
```
* The mean of the sample is `r mean(pull(df_1, samp))`.
* The mean of the logical vector is `r mean(pull(df_1, vec_logical))`.
* The mean of the character vector is `r mean(pull(df_1, vec_chara))`, showing that the mean function does not work for the character vector.
* The mean of the factor vector is `r mean(pull(df_1, vec_factor))`,, showing that the mean function does not work for the factor vector either.

## b
```{r}
convert_1 = as.numeric(pull(df_1, vec_logical))
convert_1*(pull(df_1, samp))

convert_2 = as.factor(pull(df_1, vec_logical))
convert_2*(pull(df_1, samp))

convert_3 = as.numeric(convert_2)
convert_3*(pull(df_1, samp))
```

# Question 2
## a
```{r}
df_2 = tibble(x = rnorm(500),y = rnorm(500),vec_logic = (x+y)>1,
              vec_numer = as.numeric(vec_logic),
              vec_factor = as.factor(vec_logic)
             )
```

## b
```{r}
set.seed(10086)

ggplot(df_2, aes(x = x, y = y, color = vec_logic)) + geom_point()
ggsave("df_2.png", width = 4, height = 4)
```


```{r}
ggplot(df_2, aes(x = x, y = y,color = vec_numer)) + geom_point()
ggplot(df_2, aes(x = x, y = y,color = vec_factor)) + geom_point()
```

